Proposed Solution

### 2015-12-10 proposedSolution.tex
rough approach to types of errors

\subsection{Format - Lexical}
This problem is exemplified in box (a) of the image.

\subsection{Format - Syntax}
This problem is exemplified in box (b) and (c) of the image.

\subsection{Value - Value Inconsistency}
This problem is exemplified in box (f) (g) and (h) of the image.

>>>>

\subsection{Format - Lexical}
This problem is exemplified in box (a) of the image - a certain parameter cannot contain lowercase values.
To build these rules, we collect every instance of setting that parameter over $[D]$, then infer a partition (like strisynth) on those examples.

\subsection{Format - Syntax}
This problem is exemplified in box (b) and (c) of the image.
These are ordering/dependency errors and require analysis over multiple lines.
Looking for substrings over lines can solve (b).
Not sure about (c)

\subsection{Value - Value Inconsistency}
This problem is exemplified in box (f) (g) and (h) of the image.
I don't understand (f), how can we know if query.log is a file or a table.

Interger constraints are hard to find since we dont know which ones are supposed to be coorelated.
Maybe we can build constraints between all integers in a file, then remove constraints as we see counter examples.
Is this counter-example guided synthesis?
